Preparing data from the Global Burden of Disease 2019 for METAHIT modelling

### 2021-11-24 metahit/paper_analyses.Rmd
Conflict p-value function and other scraps

pdf("../../write/prev_data.pdf", height=ht)
ggplot(gbdplot, aes(x=age, y=prev_prob, col=area, lty=gender, group=areagender)) + 
  facet_wrap(~disease, ncol=3, scales="free_y") + 
  coord_cartesian(xlim = c(50,100)) +
  ylab("Prevalence probability") + 
  xlab("Year of age") +
  geom_ribbon(aes(ymin=prev_lower, ymax=prev_upper), fill="gray80", col="gray80") +
  geom_line() + 
  labs(col = "City region", lty="") +
  theme_bw() + 
  theme(strip.text.x = element_text(size = 7.5),
        legend.spacing.y = unit(0.1, "cm"))
dev.off()

@@

## National results. Nice.
resnat %>% filter(var=="cf") %>% 
    ggplot(aes(x=`age`,y=`50%`,col=gender)) + 
    geom_line() + 
    geom_ribbon(aes(ymin=`2.5%`,ymax=`97.5%`,fill=gender)) +
    facet_wrap(~disease, nrow=2, scales="free_y")

>>>>

pdf("../../write/prev_data.pdf", height=ht)
ggplot(gbdplot, aes(x=age, y=prev_prob, col=area, lty=gender, group=areagender)) + 
  facet_wrap(~disease, ncol=3, scales="free_y") + 
  coord_cartesian(xlim = c(50,100)) +
  ylab("Prevalence") + 
  xlab("Year of age") +
  geom_ribbon(aes(ymin=prev_lower, ymax=prev_upper), fill="gray80", col="gray80") +
  geom_line() + 
  labs(col = "City region", lty="") +
  theme_bw() + 
  theme(strip.text.x = element_text(size = 7.5),
        legend.spacing.y = unit(0.1, "cm"))
dev.off()

@@

## National results.
resnat %>% filter(var=="cf") %>% 
    ggplot(aes(x=`age`,y=`50%`,col=gender)) + 
    geom_line() + 
    geom_ribbon(aes(ymin=`2.5%`,ymax=`97.5%`,fill=gender)) +
    facet_wrap(~disease, nrow=2, scales="free_y")
